Software Developers and Computers as Social Actors

### 2016-03-21 paper/draft1.tex
Minor changes to Related Works

These findings engendered a number of studies that extended on this implication by replicating, validating, and exploring the possible factors behind these kind of responses. The existing Computers as Social Actors (CASA) studies featured an implicit bias - although the studies were conducted with participants exclusively from the United States, the findings were generalized to all cultures. Katagiri and colleagues performed a comprehensive study to determine whether social rules derived from different cultures affect human users responses to computers by observing participants from the United States and Japan~\cite{katagiri2001cross}. Furthermore, researchers studied the existence of computers as social entities to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}.

@@

Software developers maintain a collaborative environment with their development machines to achieve their goals. Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present.  This type of attribution would be expected, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system. Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2008effects}. Further studies by Bickmore and Picard have documented the long-term relation establishment and maintenance between a human-computer team by observing that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}.

In this paper, we investigate whether a long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by contrasting their responses to computers with that of non-software developers.

Our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempts to determine the level of politeness software developers exhibit toward their machines.

@@

\section{Conclusion}
Although I'm not a super big fan of conclusions, it makes sense to have something short here I'd think.

>>>>

These findings engendered a number of studies that extended on this implication by replicating, validating, and exploring the possible factors behind these kind of responses. The existing Computers as Social Actors (CASA) studies featured an implicit bias - although the studies were conducted with participants exclusively from the United States, the findings were generalized to all cultures. Katagiri and colleagues performed a comprehensive study to determine whether social rules derived from different cultures affect human users responses to computers by observing participants from the United States and Japan~\cite{katagiri2001cross}. Furthermore, researchers studied the existence of computers as social entities to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}. In contrast, our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempts to determine the level of politeness software developers exhibit toward their machines.

@@

Software developers maintain a collaborative environment with their computers to complete their tasks. Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present.  This type of attribution would be expected, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system. Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2008effects}. Further studies by Bickmore and Picard have documented the long-term relation establishment and maintenance between a human-computer team by observing that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}. In this paper, we investigate whether a long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by comparing their responses to computers with that of non-software developers.

@@

\section{Conclusion}
\begin{itemize}
    \item Short brief review of the entire work and it's implications if any.
\end{itemize}
